---
title: "Linear Models"
author: "Ana María Muñoz Morales"
date: "2024-04-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Libraries are loaded

```{r}
library(readxl)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

2. Dataset is loaded.

```{r}
dataset<-read_xlsx("Correción_invernadero_Estación_Radiación.xlsx")
```

3.The "Hora" and "Pyranometer SP-Lite and CMP3 (W/m²)" columns are modified.

```{r}
dataset$Hora<-as.character(dataset$Hora)

for (i in 1:nrow(dataset)) {
  dataset$Hora[i]<-substr(dataset$Hora[i], 12,13)
}

dataset$Hora <- ifelse(dataset$Hora == "", "00", dataset$Hora)

dataset$Hora<-as.factor(dataset$Hora)

```


```{r}
dataset<-rename(dataset, Radiacion = `Pyranometer SP-Lite and CMP3 (W/m²)`)
dataset$Radiacion <- gsub(",", ".", dataset$Radiacion)
dataset$Radiacion<-as.numeric(dataset$Radiacion)
```

5. A function is created to obtain the metrics that interest us from each model.

```{r}
get_metrics_lm <- function(modelo) {
  
  R2 <- summary(modelo)$r.squared
  
  
  R2_adjusted <- summary(modelo)$adj.r.squared
  
  
  AIC_value <- AIC(modelo)
  
  # Devolver los valores como un vector
  return(c(R2 , R2_adjusted , AIC_value))
}

```


## Division of data by Temperature Sections


```{r}
dataset_1<-dataset
dataset_1$Diferencia=NULL
```


```{r}
Section1_temp <- subset(dataset_1, Fuera >= 0 & Fuera < 7.5)
Section2_temp <- subset(dataset_1, Fuera >= 7.5 & Fuera < 15)
Section3_temp<- subset(dataset_1, Fuera >= 15 & Fuera < 22.5)
Section4_temp <- subset(dataset_1, Fuera >= 22.5 & Fuera <= 30)
```

### Linear Model, Outdoor Temperature vs Greenhouse Temperature

#### Section 1 (0-7.5)

```{r}
modelo_Section1_temp<-lm(Invernadero ~ Fuera ,data=Section1_temp)
metrics_modelo_Section1_temp<-get_metrics_lm(modelo_Section1_temp)
```

#### Section 2 (7.5-15)

```{r}
modelo_Section2_temp<-lm(Invernadero ~ Fuera ,data=Section2_temp)
metrics_modelo_Section2_temp<-get_metrics_lm(modelo_Section2_temp)

```

#### Section 3 (15-22.5)

```{r}
modelo_Section3_temp<-lm(Invernadero ~ Fuera ,data=Section3_temp)
metrics_modelo_Section3_temp<-get_metrics_lm(modelo_Section3_temp)
```

#### Section 4 (22.5-30)

```{r}
modelo_Section4_temp<-lm(Invernadero ~ Fuera ,data=Section4_temp)
metrics_modelo_Section4_temp<-get_metrics_lm(modelo_Section4_temp)
```

### Linear Model, Outdoor Temperature vs Greenhouse Temperature + hours

#### Section 1 (0-7.5)

```{r}
modelo_Section1_temp_hours<-lm(Invernadero ~ Fuera + Hora,data=Section1_temp)
metrics_modelo_Section1_temp_hours<-get_metrics_lm(modelo_Section1_temp_hours)
```

#### Section 2 (7.5-15)

```{r}
modelo_Section2_temp_hours<-lm(Invernadero ~ Fuera + Hora ,data=Section2_temp)
metrics_modelo_Section2_temp_hours<-get_metrics_lm(modelo_Section2_temp_hours)
```

#### Section 3 (15-22.5)

```{r}
modelo_Section3_temp_hours<-lm(Invernadero ~ Fuera + Hora ,data=Section3_temp)
metrics_modelo_Section3_temp_hours<-get_metrics_lm(modelo_Section3_temp_hours)
```

#### Section 4 (22.5-30)

```{r}
modelo_Section4_temp_hours<-lm(Invernadero ~ Fuera + Hora ,data=Section4_temp)
metrics_modelo_Section4_temp_hours<-get_metrics_lm(modelo_Section4_temp_hours)
```


### Linear Model, Outdoor Temperature vs Greenhouse Temperature + Radiation

#### Section 1 (0-7.5)

```{r}
modelo_Section1_temp_radi<-lm(Invernadero ~ Fuera + Radiacion,data=Section1_temp)
metrics_modelo_Section1_temp_radi<-get_metrics_lm(modelo_Section1_temp_radi)
```

#### Section 2 (7.5-15)

```{r}
modelo_Section2_temp_radi<-lm(Invernadero ~ Fuera + Radiacion ,data=Section2_temp)
metrics_modelo_Section2_temp_radi<-get_metrics_lm(modelo_Section2_temp_radi)
```

#### Section 3 (15-22.5)

```{r}
modelo_Section3_temp_radi<-lm(Invernadero ~ Fuera + Radiacion ,data=Section3_temp)
metrics_modelo_Section3_temp_radi<-get_metrics_lm(modelo_Section3_temp_radi)
```

#### Section 4 (22.5-30)

```{r}
modelo_Section4_temp_radi<-lm(Invernadero ~ Fuera + Radiacion ,data=Section4_temp)
metrics_modelo_Section4_temp_radi<-get_metrics_lm(modelo_Section4_temp_radi)
```

### Linear Model, Outdoor Temperature vs Greenhouse Temperature + Radiation + hours

#### Section 1 (0-7.5)

```{r}
modelo_Section1_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora,data=Section1_temp)
metrics_modelo_Section1_temp_radi_hours<-get_metrics_lm(modelo_Section1_temp_radi_hours)
```

#### Section 2 (7.5-15)

```{r}
modelo_Section2_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora ,data=Section2_temp)
metrics_modelo_Section2_temp_radi_hours<-get_metrics_lm(modelo_Section2_temp_radi_hours)
```

#### Section 3 (15-22.5)

```{r}
modelo_Section3_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora ,data=Section3_temp)
metrics_modelo_Section3_temp_radi_hours<-get_metrics_lm(modelo_Section3_temp_radi_hours)
```

#### Section 4 (22.5-30)

```{r}
modelo_Section4_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora  ,data=Section4_temp)
metrics_modelo_Section4_temp_radi_hours<-get_metrics_lm(modelo_Section4_temp_radi_hours)
```


## Division of data by Month Sections

```{r}
dataset_2<-dataset
dataset_2$Diferencia=NULL
```

```{r}
for (i in 1:nrow(dataset_2)) {
  name_num <- substr(dataset_2$`Fecha-Hora`[i], 6, 7)
  name_month <- switch(name_num,
                       "01" = "january",
                       "02" = "february",
                       "03" = "march",
                       "12" = "december",
                       "Not Found")
  dataset_2$Month[i] <- name_month
}
```

```{r}
Section1_month <- subset(dataset_2, Month=="december")
Section2_month <- subset(dataset_2, Month=="january")
Section3_month <- subset(dataset_2, Month=="february")
Section4_month <- subset(dataset_2, Month=="march")
```


### Linear Model, Outdoor Temperature vs Greenhouse Temperature

#### Section 1 (December)

```{r}
modelo_Section1_month_temp<-lm(Invernadero ~ Fuera ,data=Section1_month)
metrics_modelo_Section1_month_temp<-get_metrics_lm(modelo_Section1_month_temp)
```

#### Section 2 (January)

```{r}
modelo_Section2_month_temp<-lm(Invernadero ~ Fuera ,data=Section2_month)
metrics_modelo_Section2_month_temp<-get_metrics_lm(modelo_Section2_month_temp)
```

#### Section 3 (February)

```{r}
modelo_Section3_month_temp<-lm(Invernadero ~ Fuera ,data=Section3_month)
metrics_modelo_Section3_month_temp<-get_metrics_lm(modelo_Section3_month_temp)
```

#### Section 4 (March)

```{r}
modelo_Section4_month_temp<-lm(Invernadero ~ Fuera ,data=Section4_month)
metrics_modelo_Section4_month_temp<-get_metrics_lm(modelo_Section4_month_temp)
```


### Linear Model, Outdoor Temperature vs Greenhouse Temperature + hours

#### Section 1 (December)

```{r}
modelo_Section1_month_temp_hours<-lm(Invernadero ~ Fuera + Hora,data=Section1_month)
metrics_modelo_Section1_month_temp_hours<-get_metrics_lm(modelo_Section1_month_temp_hours)
```

#### Section 2 (January)

```{r}
modelo_Section2_month_temp_hours<-lm(Invernadero ~ Fuera + Hora,data=Section2_month)
metrics_modelo_Section2_month_temp_hours<-get_metrics_lm(modelo_Section2_month_temp_hours)
```

#### Section 3 (February)

```{r}
modelo_Section3_month_temp_hours<-lm(Invernadero ~ Fuera + Hora,data=Section3_month)
metrics_modelo_Section3_month_temp_hours<-get_metrics_lm(modelo_Section3_month_temp_hours)
```

#### Section 4 (March)

```{r}
modelo_Section4_month_temp_hours<-lm(Invernadero ~ Fuera + Hora,data=Section4_month)
metrics_modelo_Section4_month_temp_hours<-get_metrics_lm(modelo_Section4_month_temp_hours)
```


### Linear Model, Outdoor Temperature vs Greenhouse Temperature + Radiation

#### Section 1 (December)

```{r}
modelo_Section1_month_temp_radi<-lm(Invernadero ~ Fuera + Radiacion,data=Section1_month)
metrics_modelo_Section1_month_temp_radi<-get_metrics_lm(modelo_Section1_month_temp_radi)
```

#### Section 2 (January)

```{r}
modelo_Section2_month_temp_radi<-lm(Invernadero ~ Fuera + Radiacion,data=Section2_month)
metrics_modelo_Section2_month_temp_radi<-get_metrics_lm(modelo_Section2_month_temp_radi)
```

#### Section 3 (February)

```{r}
modelo_Section3_month_temp_radi<-lm(Invernadero ~ Fuera + Radiacion,data=Section3_month)
metrics_modelo_Section3_month_temp_radi<-get_metrics_lm(modelo_Section3_month_temp_radi)
```

#### Section 4 (March)

```{r}
modelo_Section4_month_temp_radi<-lm(Invernadero ~ Fuera + Radiacion,data=Section4_month)
metrics_modelo_Section4_month_temp_radi<-get_metrics_lm(modelo_Section4_month_temp_radi)
```

### Linear Model, Outdoor Temperature vs Greenhouse Temperature + Radiation +hours

#### Section 1 (December)

```{r}
modelo_Section1_month_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora,data=Section1_month)
metrics_modelo_Section1_month_temp_radi_hours<-get_metrics_lm(modelo_Section1_month_temp_radi_hours)

```


#### Section 2 (January)

```{r}
modelo_Section2_month_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora,data=Section2_month)
metrics_modelo_Section2_month_temp_radi_hours<-get_metrics_lm(modelo_Section2_month_temp_radi_hours)
```


#### Section 3 (February)

```{r}
modelo_Section3_month_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora,data=Section3_month)
metrics_modelo_Section3_month_temp_radi_hours<-get_metrics_lm(modelo_Section3_month_temp_radi_hours)

```


#### Section 4 (March)

```{r}
modelo_Section4_month_temp_radi_hours<-lm(Invernadero ~ Fuera + Radiacion + Hora,data=Section4_month)
metrics_modelo_Section4_month_temp_radi_hours<-get_metrics_lm(modelo_Section4_month_temp_radi_hours)

```



### Comparative table

```{r,echo=FALSE}
table <-data.frame(Model= c("Temp_rang1","Temp_rang2","Temp_rang3","Temp_rang4","Temp_hours_rang1","Temp_hours_rang2","Temp_hours_rang3","Temp_hours_rang4","Temp_radi_rang1","Temp_radi_rang2","Temp_radi_rang3","Temp_radi_rang4","Temp_radi_hours_rang1","Temp_radi_hours_rang2","Temp_radi_hours_rang3","Temp_radi_hours_rang4","Temp_december","Temp_january","Temp_february","Temp_march","Temp_hours_december","Temp_hours_january","Temp_hours_february","Temp_hours_march","Temp_radi_december","Temp_radi_january","Temp_radi_february","Temp_radi_march","Temp_radi_hours_december","Temp_radi_hours_january","Temp_radi_hours_february","Temp_radi_hours_march"),R2=c(metrics_modelo_Section1_temp[1],metrics_modelo_Section2_temp[1],metrics_modelo_Section3_temp[1],metrics_modelo_Section4_temp[1],metrics_modelo_Section1_temp_hours[1],metrics_modelo_Section2_temp_hours[1],metrics_modelo_Section3_temp_hours[1],metrics_modelo_Section4_temp_hours[1],metrics_modelo_Section1_temp_radi[1],metrics_modelo_Section2_temp_radi[1],metrics_modelo_Section3_temp_radi[1],metrics_modelo_Section4_temp_radi[1],metrics_modelo_Section1_temp_radi_hours[1],metrics_modelo_Section2_temp_radi_hours[1],metrics_modelo_Section3_temp_radi_hours[1],metrics_modelo_Section4_temp_radi_hours[1],metrics_modelo_Section1_month_temp[1],metrics_modelo_Section2_month_temp[1],metrics_modelo_Section3_month_temp[1],metrics_modelo_Section4_month_temp[1],metrics_modelo_Section1_month_temp_hours[1],metrics_modelo_Section2_month_temp_hours[1],metrics_modelo_Section3_month_temp_hours[1],metrics_modelo_Section4_month_temp_hours[1],metrics_modelo_Section1_month_temp_radi[1],metrics_modelo_Section2_month_temp_radi[1],metrics_modelo_Section3_month_temp_radi[1],metrics_modelo_Section4_month_temp_radi[1],metrics_modelo_Section1_month_temp_radi_hours[1],metrics_modelo_Section2_month_temp_radi_hours[1],metrics_modelo_Section3_month_temp_radi_hours[1],metrics_modelo_Section4_month_temp_radi_hours[1]),
                  R2_adjusted=c(metrics_modelo_Section1_temp[2],metrics_modelo_Section2_temp[2],metrics_modelo_Section3_temp[2],metrics_modelo_Section4_temp[2],metrics_modelo_Section1_temp_hours[2],metrics_modelo_Section2_temp_hours[2],metrics_modelo_Section3_temp_hours[2],metrics_modelo_Section4_temp_hours[2],metrics_modelo_Section1_temp_radi[2],metrics_modelo_Section2_temp_radi[2],metrics_modelo_Section3_temp_radi[2],metrics_modelo_Section4_temp_radi[2],metrics_modelo_Section1_temp_radi_hours[2],metrics_modelo_Section2_temp_radi_hours[2],metrics_modelo_Section3_temp_radi_hours[2],metrics_modelo_Section4_temp_radi_hours[2],metrics_modelo_Section1_month_temp[2],metrics_modelo_Section2_month_temp[2],metrics_modelo_Section3_month_temp[2],metrics_modelo_Section4_month_temp[2],metrics_modelo_Section1_month_temp_hours[2],metrics_modelo_Section2_month_temp_hours[2],metrics_modelo_Section3_month_temp_hours[2],metrics_modelo_Section4_month_temp_hours[2],metrics_modelo_Section1_month_temp_radi[2],metrics_modelo_Section2_month_temp_radi[2],metrics_modelo_Section3_month_temp_radi[2],metrics_modelo_Section4_month_temp_radi[2],metrics_modelo_Section1_month_temp_radi_hours[2],metrics_modelo_Section2_month_temp_radi_hours[2],metrics_modelo_Section3_month_temp_radi_hours[2],metrics_modelo_Section4_month_temp_radi_hours[2]),AIC=c(metrics_modelo_Section1_temp[3],metrics_modelo_Section2_temp[3],metrics_modelo_Section3_temp[3],metrics_modelo_Section4_temp[3],metrics_modelo_Section1_temp_hours[3],metrics_modelo_Section2_temp_hours[3],metrics_modelo_Section3_temp_hours[3],metrics_modelo_Section4_temp_hours[3],metrics_modelo_Section1_temp_radi[3],metrics_modelo_Section2_temp_radi[3],metrics_modelo_Section3_temp_radi[3],metrics_modelo_Section4_temp_radi[3],metrics_modelo_Section1_temp_radi_hours[3],metrics_modelo_Section2_temp_radi_hours[3],metrics_modelo_Section3_temp_radi_hours[3],metrics_modelo_Section4_temp_radi_hours[3],metrics_modelo_Section1_month_temp[3],metrics_modelo_Section2_month_temp[3],metrics_modelo_Section3_month_temp[3],metrics_modelo_Section4_month_temp[3],metrics_modelo_Section1_month_temp_hours[3],metrics_modelo_Section2_month_temp_hours[3],metrics_modelo_Section3_month_temp_hours[3],metrics_modelo_Section4_month_temp_hours[3],metrics_modelo_Section1_month_temp_radi[3],metrics_modelo_Section2_month_temp_radi[3],metrics_modelo_Section3_month_temp_radi[3],metrics_modelo_Section4_month_temp_radi[3],metrics_modelo_Section1_month_temp_radi_hours[3],metrics_modelo_Section2_month_temp_radi_hours[3],metrics_modelo_Section3_month_temp_radi_hours[3],metrics_modelo_Section4_month_temp_radi_hours[3]))
```


```{r}
table
```


## Data corrections


1. The datastet to be corrected is loaded.

```{r}
dataset_to_correct<-read_xlsx("Brutos Fuera Invernadero Santomera 2023-2024.xlsx")
```


2. The data in the dataset are adapted.

```{r}
dataset_to_correct$Time<-as.character(dataset_to_correct$Time)

for (i in 1:nrow(dataset_to_correct)) {
  dataset_to_correct$Time[i]<-substr(dataset_to_correct$Time[i], 12,13)
}

dataset_to_correct$Time <- ifelse(dataset_to_correct$Time == "", "00", dataset_to_correct$Time)

dataset_to_correct$Time<-as.factor(dataset_to_correct$Time)
dataset_to_correct$`Relative Humidity (% RH)`=NULL
dataset_to_correct$`Lluvia desde26Feb2021 (mm)`=NULL
dataset_to_correct<-dataset_to_correct %>% rename (Hora = Time, `Fecha-Hora` = Date)
```


3. We filter data and modify the dataset for further use.

```{r}
dataset_to_correct$`Fecha-Hora` <- as.Date(dataset_to_correct$`Fecha-Hora`)
dataset_to_correct_2 <- dataset_to_correct %>%
  filter(`Fecha-Hora` >= as.Date("2023-12-01") & `Fecha-Hora` <= as.Date("2024-03-21"))
dataset_to_correct_2 <- dataset_to_correct_2 %>%
  slice(-(10722
:10753))

```


```{r}

dataset_to_correct_2 <- dataset_to_correct_2 %>%
  group_by(`Fecha-Hora`, Hora) %>%
  summarize(Radiacion
            = mean(`Pyranometer SP-Lite and CMP3 (W/m²)`),
            Fuera = mean(`Air temperature (°C)`))


```



```{r}
for (i in 1:nrow(dataset_to_correct_2)) {
  name_num <- substr(dataset_to_correct_2$`Fecha-Hora`[i], 6, 7)
  name_month <- switch(name_num,
                       "01" = "january",
                       "02" = "february",
                       "03" = "march",
                       "12" = "december",
                       "Not Found")
  dataset_to_correct_2$Month[i] <- name_month
}
```

4. We section the data by month

```{r}
Data1_month <- subset(dataset_to_correct_2, Month=="december")
Data2_month <- subset(dataset_to_correct_2, Month=="january")
Data3_month <- subset(dataset_to_correct_2, Month=="february")
Data4_month <- subset(dataset_to_correct_2, Month=="march")
```

5. The values predicted by the model are obtained using the *predict()* function.


```{r}
predicciones_1 <- predict(modelo_Section1_month_temp_radi_hours, Data1_month)
Data1_month$Invernadero <- predicciones_1
```

```{r}
predicciones_2 <- predict(modelo_Section2_month_temp_radi_hours, Data2_month)
Data2_month$Invernadero <- predicciones_2
```

```{r}
predicciones_3 <- predict(modelo_Section3_month_temp_radi_hours, Data3_month)
Data3_month$Invernadero <- predicciones_3
```


```{r}
predicciones_4 <- predict(modelo_Section4_month_temp_radi_hours, Data4_month)
Data4_month$Invernadero <- predicciones_4
```

6. The final corrected dataset is created.

```{r}
dataset_final<-rbind(Data1_month,Data2_month,Data3_month,Data4_month)
```

```{r}
write.csv(dataset_final, "Brutos Fuera Invernadero Santomera2023-2024_Corregido.csv", row.names = FALSE)
```